%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[sfdefault,light]{roboto}  %% Option 'sfdefault' only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\name{Leonardo V. Castorina} % Your name
\begin{document}
{\centering
    \href{https://github.com/universvm}{\faGithub \ universvm} \ \ \   
\href{https://www.linkedin.com/in/leonardo-castorina/}{\faLinkedin \ in/leonardo-castorina} \ \ \  
{\faPhone \ +44 7766 06 2571} \ \ \   
 \href{mailto:leonardo.castorina98@gmail.com}{\faEnvelope \ leonardo.castorina98@gmail.com}
\par}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Osmitau Technologies}{Mar 2019 - Jun 2020}{– CEO \& Co-Founder}{Edinburgh (Scotland)}
\item Developed a machine-learning drowsiness detection tool for the
automotive industry.
\item Co-authored a white paper on automotive safety to explore the state of
the field. \fontsize{8pt}{12pt}\selectfont\href{https://osmitau.com/solutions
.html}{ \faGlobe \ Read Here}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IBM}{Jun 2019 - Sep 2019}{– Extreme Blue Technical Intern}{Hursley (UK)}
\item Built a search-planning interface for the search of vulnerable missing people with the UK police. 
\item Used LSTM, Convolutional Neural Networks (CNN), OpenStreetMap and statistics to derive an adaptive location radius which saved $\sim$1.5 hours per search.
\end{rSubsection}

%------------------------------------------------


\begin{rSubsection}{P\&G}{Jul 2018 - Sep 2018}{– R\&D Intern (Personal Healthcare)}{Egham (UK)}
\item Analysed the literature to verify the health benefits of a range of products. 
\item Planned a market and consumer research to identify the best strategy to enter the market. 
\item Designed a prototype app using Sketch to test customer behaviour.


\end{rSubsection}

%------------------------------------------------


\begin{rSubsection}{Swiss Institute of Bioinformatics}{May 2017 - Jul 2017}{– Data Visualization Intern}{Geneva (Switzerland)}
\item Redesigned ancestor graph for protein entries in \href{https://www.nextprot.org}{NeXtProt}. \fontsize{8pt}{12pt}\selectfont \href{https://github.com/universvm/nextprot-ancestor-graph}{ \faGithub \ View on Github}
\normalsize \item Developed Polymer.js components for
\href{https://glyconnect.expasy.org}{GlyConnect} to represent biological data.
\fontsize{8pt}{12pt}\selectfont
\href{https://github.com/universvm/glyco-balls}{ \faGithub \ View on Github}
\end{rSubsection}

%------------------------------------------------


\end{rSection}


\begin{rSection}{Projects}

\begin{rSubsection}{Dissertation: Explainable Deep Learning for {\it de novo} Protein Design (Currently Publishing)}{}{}{}
\item Used 3D CNN to predict the identity of the residues required to obtain a protein shape. 
\item Explored explainability using activation maps and visualized accuracy and precision with Pymol.
\item Obtained accuracies of up to 40\% and consistently better than alternative methods.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Aposteriori - Protein Structures Voxelisation for Deep Learning}{\fontsize{8pt}{12pt}\selectfont \href
{https://github.com/wells-wood-research/aposteriori}{ \faGithub \ View on Github}}{}{}
\item Co-created a library for the voxelization of protein structures for protein design from PDB files. 
\item Implemented parallel processesing, atom encodings, gaussian representations and a CLI.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Medical Search Engine (Group Project - Ongoing)}{}{}

\item Indexing a dataset of 100+ GB and optimizing: storage, vectorization and speed to enable researchers to explore medical literature more efficiently
\item Using NLP machine learning and statistics to classify query to speed up search. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MRI Scan Super-Resolution (Group Project - Ongoing)}{}{}

\item Using Deep Learning methods on PyTorch to upsample low-res scans from the NHS to improve and speed up diagnosis.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{\bf The University of Edinburgh} \hfill {\em} \\ 
\item MScR. Biomedical Artificial Intelligence (1st Class)\hfill {Sep 2020
\em - Present}
\item BSc. (Hons) Biochemistry (2.1 Class) \hfill {Sep 2016 - May 2020}
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Patents \& Publications}

\textbf{Castorina, L. V.}, (2021). \textit{Patent Filed with IBM}. Patent Pending.

\end{rSection}

%----------------------------------------------------------------------------------------
%	Languages SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Languages}

%English (Fluent), Italian (Fluent), French (DELFB2) 
%\end{rSection}

\fontsize{8pt}{12pt}\selectfont
\begin{flushright}
Last updated: \today \ \  \href{https://github.com/universvm/cv}{Latest: https://github.com/universvm/cv}
\end{flushright}

\end{document}
